---
title: "A More Elaborate Example"
output: html_document
---

### Question
Is the percentage of smokers significantly different between groups of patients?

### Data

```{r prop_test, comment="", echo=FALSE}
smokers  <- c( 80, 84, 129, 90)
patients <- c( 86, 93, 136, 120)

smokers_percent <- paste0(round(smokers/patients * 100,1),"%")

conf.level <- 0.99
results <- prop.test(smokers,
                     patients,
                     conf.level = conf.level)

estimates <- paste(round(results$estimate * 100,1),"%",
                   collapse=" vs. ",
                   sep="")


p_value <- ifelse(results$p.value < .001,
                  0.001,
                  round(results$p.value,3))

p_eq_lt <- ifelse(p_value > .001,
                  "=",
                  "<")

p_sig <- ifelse(p_value > 1-conf.level,
                "not",
                "")


```



```{r table, results='asis', echo=FALSE}
mydata <- data.frame(Smokers = smokers,
                     Total_Patients = patients,
                     Percent_Smokers = smokers_percent)

knitr::kable(mydata,
             row.names = TRUE,
             align = c('c', 'c', 'c'))
```

### Results
This example includes the smoking status from `r length(patients)` groups of patients. ${\chi}^2$ analysis of the proportion of smokers vs non-smokers indicate they are `r p_sig` significantly different between groups (`r estimates`, $p$-value `r paste(p_eq_lt, p_value)`, `r paste0(round(conf.level*100,0),"%")` confidence level).


```{r prop_test_results, eval=FALSE, echo=FALSE, comment="   "}

results
```


